---
title: "Assign4-Part2"
author: "KunalRelia"
date: "April 12, 2016"
output: html_document
---

Q2)CRAWLING TWITTER

a + b +c{combined})
setup credentials:

```{r}
require(twitteR)
require(RCurl)
consumer_key <-'jjIPimGE10JIOHFA2ZT6TGRXR'
consumer_secret <-'gDtvw9o4fg7j93bKDD0S1zaBZ6D1aTJ7LR7BCuhSCWfYQzHitc'
access_token <-'131157917-vRx5IuLyH52pZ8RvGI5PA0NWeY0CmBSSjSF4qoZr'
access_secret <-'mfkKcSBtDTwDzwdIScHKcgv6F1lAOxadw8zPoBwTdHW3q'
setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```

search using keywords:

```{r, echo=FALSE}
myTweets <- searchTwitter("#SXSW2016", n=200, lang="en")
myTweets
```

Extract the usernames:
```{r}
k = 100
tweetsDF <- twListToDF(myTweets)
nameDF <- tweetsDF[, c("screenName")]
uniqueNameDF <- unique(nameDF)
hundredNamesDF <- head(uniqueNameDF, k)
hundredNamesDF
```

```{r}
require(networkD3)
require(igraph)
network_tw <- data.frame(src=character(), target=character(), stringsAsFactors=FALSE) 
for(i in 1:100)
{
    start <- getUser(uniqueNameDF[i],retryOnRateLimit=900)
    friends.object<-lookupUsers(start$getFriendIDs(retryOnRateLimit=900))
    follower.object<-lookupUsers(start$getFollowerIDs(retryOnRateLimit=900))
    
    n<- length(friends.object)
    m<- length(follower.object)
    
    friends <- sapply(friends.object[1:n],screenName)
    followers <- sapply(follower.object[1:m],screenName)
    
    networkData <- data.frame(src=uniqueNameDF[i], target=friends)
    network_tw <- merge(network_tw, networkData,  all=T)
    networkData <- data.frame(src=followers, target=uniqueNameDF[i])
    network_tw <- merge(network_tw, networkData,  all=T)
}

# degree assess
g <- graph.data.frame(network_tw, directed = F)

degree(g, mode = "total")

degree_distribution(g)

plot(degree_distribution(g))

# Plot
simpleNetwork(network_tw, zoom = T, linkDistance = 60, opacity = 0.5, linkColour = "grey", nodeColour = "purple",
  nodeClickColour = "red", textColour = "blue")

```
Conclusion:
Shown above is the twitter network of users who have tweeted on the topic "SXSW2016".
The reason I have chosen this metric is that it helps in better visualization. 
Also if a person "A" is following a person "B", then there will be an edge from A->B. This will help us because the in-degree of "B" will tell us the number of followers he/she has.
