---
title: "Assign4"
author: "KunalRelia"
date: "April 12, 2016"
output: html_document
---

Q1)

a)Read in the files and visualize the network (try using ggplot2 or networkD3 libraries).

```{r}
#using networkD3 to create the network
library(networkD3)

#reading and storing vertices
vertex<-read.table(file.choose(),sep="\t")
colnames(vertex)<-c("id","item")

#reading and storing edges
edge<-read.table(file.choose(),sep="\t")
colnames(edge)<-c("src","dest")

require("sqldf")

#change the ids to names for network readability

sourcenames<-sqldf("select item from edge,vertex where id=src")
destnames<-sqldf("select item from edge,vertex where id=dest")

graphName <- cbind(sourcenames,destnames)
colnames(graphName)<-c("srcWithName","destWithName")

#store the information in data frame and draw the network
data<-data.frame(graphName$srcWithName,graphName$destWithName)
simpleNetwork(data)

```

Conclusion:
As per the requirement, we have read the files and created the network.

b) Calculate the degree centrality of each node.

```{r}
#use igraph to calculate the degree centrality of each node
library(igraph)

#calculate the degree of centrality
network<-graph.data.frame(edge,vertex,directed=T)
centrality<-centralization.degree(network)
centralityDF<-data.frame(centrality$res)
View(centralityDF)

```

Conclusion:
The above generated View gives us the degree centrality of each node in the network.

d) Which are the most connected nodes?
```{r}
#appending an index column to determine which node has the highest centrality
id <- rownames(centralityDF)
centralityDF <- cbind(id=id, centralityDF)

#sort the centrality by decreasing order
centralityDF[order(centralityDF$centrality.res,decreasing = TRUE),]
```

Conclusion:
From the above written command, the top 5 connected nodes are:
2             33
12             29
79             29
21             24
31             23

c)Visually determine what are the furthest ingredients from cocoa powder.
```{r}
#visualization by docomposition of graph - Disjoint network nodes are colored differently
dg<-decompose.graph(network)
plot(dg[0],dg[1])
#vertex.connectivity(network)

#Visually, the vertices that are NOT connected to cocoa powder are the furthest. We will calculate the shortest path of all nodes from cocoa powder to validate our claim
network<-graph.data.frame(edge,vertex,directed=T)
centrality<-centralization.degree(network)
centralityDF<-data.frame(centrality$res)
dist <- shortest.paths(network, v=408)
max<-0
farthest<-c()
count<-0

for(i in 1:562){
  if(dist[i][1]==Inf && !is.na(dist[i][1]))
  {
  count<-count+1
  farthest<-union(farthest,c(i))
  }
}
farthest

#based on above list, we will select the names based on node id.
require(sqldf)
collnames<-sqldf("select item from vertex where id in (93,94,107,108,109,110,111,113,114,256,353,431,432,459,460,463,464,480,481)")
View(collnames)
```

Conclusion:
As per visualization and above validation, following vertices are the farthest :
item
1marshmallow
2marshmallow creme
3yellow mustard
4honey mustard
5mustard
6dijon mustard
7spicy brown mustard
8mussel
9clam
10mustard powder
11mustard seed
12pound cake
13angel food cake
14toothpick
15skewer
16baking mix
17pancake mix
18avocado
19guacamole